---
title: "Practical 2 Worksheet"
output: html_document
---

Use this workspace to complete the Visualization Practical. 

---

Install Packages if needed:
```{r}
install.packages("tidyverse")
```

Load packages in the local library:
```{r}
library(tidyverse)

```

---
---

**Question 1: Run the following code examples, and identify which is the most easily understood.**

---

Copy and Paste each code block here:
```{r}

dia.ex1 <- ggplot(data = diamonds, mapping = aes(x = price, y = carat)) +
  geom_point() + 
  labs(x = "Price in USD", y = "Carat", title = "Price of Diamond by Carat") + 
  theme_classic()

dia.ex1

dia.ex2 <- ggplot(data = diamonds, mapping = aes(x = price, y = carat,
                                                            colour = cut)) +
  geom_point(shape=1) + 
  labs(x = "Price in USD", y = "Carat", title = "Price of Diamond by Carat") + 
  theme_minimal()

dia.ex3 <- dia.ex2 + facet_grid(cols = vars(diamonds$cut))

dia.ex2

```


---

**Question 2a: Using your knowledge and understanding of what makes a good, clear graph, improve the graph which you consider to be the worst.**

---

Copy and Paste your code here and edit accordingly
```{r}

ggplot(data = diamonds,                   #
       mapping = aes(                     #
         x = price,                       #
         y = carat,                       #
         colour = clarity)) +                #links clarity column to color                 #links cut column to the shape 
  geom_point() +                          #
  labs(                                   #
    x = "Price in USD",                   #
    y = "Carat of Diamond",               #
    title = "Price of Diamond per Carat", #
    colour = "Diamond Clarity",           # adding a title to the clarity legend
    shape = "Diamond Cut") +              #adding a title to the shape item legend
  theme_minimal()          


```

---

**Question 2b: Now using your knowledge and understanding, make a good, clear graph worse.**

---

Copy and Paste your code here and edit accordingly
```{r}

ggplot(data = diamonds,                   #
       mapping = aes(                     #
         x = price,                       #
         y = carat,                       #
         alpha = clarity,                #links clarity column to color
         shape = cut,
         size = cut)) +                  #links cut column to the shape 
  geom_line() +                          #
  labs(                                   #
    x = "Price in USD",                   #
    y = "Carat of Diamond",               #
    title = "Price of Diamond per Carat", #
    colour = "Diamond Clarity",           # adding a title to the clarity legend
    shape = "Diamond Cut") +              #adding a title to the shape item legend
  theme_minimal()          

```


---

**Question 3a: Within each of the following code examples, identify what each layer does within the graph**

---

1. Add Comments for each line in the function
```{r}
ggplot(data = diamonds,                    #determines which dataframe we use
       mapping = aes(                      #set of columns mapped to parts of the plot
         x = price,                        #linking x to the price column
         y = carat)) +                     #linking y to the carat column
  geom_point() +                           #identifying what we want to see in the plot (points)
  labs(                                    #labels
    x = "Price in USD",                    #label for x axis
    y = "Carat of Diamond",                #label for y axis
    title = "Price of Diamond per Carat")  #setting the title
 
```

2. Add Comments for each line in the function
```{r}
ggplot(data = diamonds,                   #
       mapping = aes(                     #
         x = price,                       #
         y = carat,                       #
         colour = clarity,                #links clarity column to color
         shape = cut)) +                  #links cut column to the shape 
  geom_point() +                          #
  labs(                                   #
    x = "Price in USD",                   #
    y = "Carat of Diamond",               #
    title = "Price of Diamond per Carat", #
    colour = "Diamond Clarity",           # adding a title to the clarity legend
    shape = "Diamond Cut") +              #adding a title to the shape item legend
  theme_minimal()                         #setting a theme to make it prettier
```

---

**Question 3b: Using the previous examples as a basis, attempt to reproduce the plot in the HTML file**

---

Use this block to reproduce the graph
```{r}
ggplot(data = mpg,                   #
       mapping = aes(                     #
         x = cty,                       #
         y = hwy,                       #
         colour = cyl,                #links clarity column to color
         shape = drv)) +                  #links cut column to the shape 
  geom_point() +                          #
  labs(                                   #
    x = "City Miles per Gallon",                   #
    y = "Highway Miles per Gallon",               #
    title = "The Number of City Miles per Gallon, compared with the number\n   of Highway miles per Gallon", #
    colour = "Number of Cylinders",           # adding a title to the clarity legend
    shape = "Type of Drive") +              #adding a title to the shape item legend
  theme_minimal()    
```

---

**Question 4: Using your previous knowledge of faceting and the examples above, change the following code examples so that it converts it from a complex scatter plot, to a series of faceted plots.**

---

Change this code accordingly:
```{r}
ggplot(data = msleep, 
       mapping = aes(x = sleep_rem, y = awake, size = brainwt)) + 
        geom_point() + 
        labs(x = "Amount of REM Sleep", y = "Amount of Time Spent Awake",
             title = "Amount of REM Sleep compared to the Time Spent Awake",
             colour = "Diet") +
        facet_grid(cols = vars(vore)) +
        theme_minimal()
```


---

**Question 5: Under each tab (in the HTML file), examine the different graphs produced using the same information, which best displays the information present.**

Graph set 1; They ar both continuous. A line-graph makes no sense, as there isn't a clear 'line' to follow. The heat-map is nice, as it shows how many dots are in a given part of the graph. Th ebar-graph suchs as it only shows that there are more cheap diamonds, which isn't necessarily interesting. Heat map has best info-ink
Graph set 2: categorical type of car and miles per gallon is continuous. Bar graph shows interesting stuff. Scatterplot/lineplot are terrible. 
Graph set 3: Scatterplot is best! 
---

**Question 6: Follow the steps to plot the course of these stock prices over six months** 

---

Following the steps on HTML file, plot the data below.

  Step Zero:
```{r}
aapl.stk <- read_csv(file = "data/HistoricalData_AAPI_6m.csv")
msft.stk <- read_csv(file = "data/HistoricalData_MSFT_6m.csv")
fb.stk <- read_csv(file = "data/HistoricalData_FB_6m.csv")
```

  Step One
```{r}
aapl.stk$`Close/Last` <- as.numeric(gsub("\\$", "", aapl.stk$`Close/Last`))
msft.stk$`Close/Last` <- as.numeric(gsub("\\$", "", msft.stk$`Close/Last`))
fb.stk$`Close/Last`   <- as.numeric(gsub("\\$", "", fb.stk$`Close/Last`))
aapl.stk$Date<- as.Date(aapl.stk$Date,format='%m/%d/%Y')
msft.stk$Date<- as.Date(msft.stk$Date,format='%m/%d/%Y')
fb.stk$Date<- as.Date(fb.stk$Date,format='%m/%d/%Y')
```

  Step Two
```{r}
ggplot(data = aapl.stk, mapping = aes(x=Date, y = Volume)) + geom_line()
ggplot(data = msft.stk, mapping = aes(x=Date, y = Volume)) + geom_line()
ggplot(data = fb.stk, mapping = aes(x=Date, y = Volume)) + geom_line()
```

  Step Three & Four
```{r}
ggplot() +
  geom_line(data = aapl.stk, mapping = aes(x=Date, y = Volume, color = 'blue')) +
  geom_line(data = msft.stk, mapping = aes(x=Date, y = Volume, color = 'red')) +
  geom_line(data = fb.stk, mapping = aes(x=Date, y = Volume, color = 'green')) +
  scale_color_discrete(name = 'Type of stock', 
                     labels = c('aapl','msft','fb')) +
   theme_minimal()
```

---

**Question 7a: After exploring the huge amount of colour platettes available, use the provided template and change the scale colour.**

---

```{r}
library(ghibli)
ggplot(data = airquality, mapping = aes(x = Wind, y = Solar.R, colour = Temp)) +
  geom_point() + scale_colour_ghibli_c('KikiMedium')
    #Colour Function
```

--- 

**Question 7b: using the dataset midwest (from ggplot); produce a density plot which examines the density of a specific variable of your choosing, grouped by another variable from the dataset, using this information regarding colours for density plots.**

---

```{r}
ggplot(data = midwest ) +
  geom_density(aes(x = area, color = state) ) + scale_colour_ghibli_d('KikiMedium') 

```

---

**Question 8: Using the dataset msleep, plot sleep_rem against awake, including brainwt as the size and vore as the shape**

---

```{r}
ggplot(data = msleep, mapping = aes(x = sleep_rem, y = awake, size = brainwt, shape = vore)) +
  geom_point() + theme_minimal() + scale_colour_ghibli_d('KikiMedium') 

```

---

**Question 9a: Using the template provided, add in sufficient labels too all the data included**

---

```{r}
ggplot(data = mpg, 
       mapping = aes(x = displ, y = cty, shape = drv, colour = fl)) +
    geom_point() + 
    theme_minimal() + 
  labs( # Added these labels to the code
    x = "Engine Displacement (ltrs)",
    y = 'City Miles per Gallon',
    shape = 'Type of Drive',
    colour = 'Type of Fuel',
    title = 'Displacement vs Miles per Gallon'
  )

```

---

**Question 9b: Using the stock graph you produced in Question 6, using annotate highlight a period of time (for example “2019-11-01” - “2020-01-01”) and a specific data (for example “2020-14-02”).**

---

```{r}
ggplot() +
  geom_line(data = aapl.stk, mapping = aes(x=Date, y = `Close/Last`, color = 'blue')) +
  geom_line(data = msft.stk, mapping = aes(x=Date, y = `Close/Last`, color = 'red')) +
  geom_line(data = fb.stk, mapping = aes(x=Date, y = `Close/Last`, color = 'green')) +
  scale_color_discrete(name = 'Type of stock', 
                     labels = c('Apple','Microsoft','Facebook')) +
   theme_minimal() +
  annotate(geom = "rect", xmin = as.Date("2021-03-01"), xmax = as.Date("2021-04-01"), ymin = 0, ymax = 320, fill = "red", alpha = 0.2) +
  annotate(geom = "text", x = as.Date("2021-03-16"), y = 50, label = "Spring \n 2021")

```

---

**Question 10: Using all of the skills, templates and materials covered, as well as your own knowledge, using one of the following datasets available within ggplot, produce your own graph expressing some of the information within it.**

---

```{r}


```