---
title: "Practical 2 Worksheet"
output: html_document
---

Use this workspace to complete the Visualization Practical. 
Vivian van Oosten
Cedric Gevers 80051003


---

Load packages in the local library:
```{r}
library(tidyverse)
library(ghibli)

```

We used the midwest data set and wanted to know what the % below poverty was. 
the fist step was looking at the data set and selecting the parameters used for our visualisation. 

```{r}
summary(midwest)
show(midwest)
```


Subsett is made for Michagan and Ohio
```{r}
il_in <- c("MI", "OH")
```

In the graph below we used the histogram function to compare MI and OH to each other
```{r}
p <- ggplot(data = subset(midwest, subset = state %in% il_in),
            mapping = aes(x = percbelowpoverty, fill = state))
p + geom_histogram(alpha = 0.4, bin = 30)+
scale_fill_brewer(palette = 'Dark2', direction = 10)+
scale_color_discrete(name = 'State',
labels = c('Statename1','Statename2')) 


```

 Our final graph is a density plot of MI and OH where its easy to see the differance between the 2. Now you can clearly see that the citys in Michigan have a higher child poverty rate than Ohio. 

```{r}

    
il_in <- c("OH", "MI")
ggplot(data = subset(midwest, subset = state %in% il_in),
mapping = aes(x = percchildbelowpovert, fill = state)) +
geom_density(alpha = 0.4, bins = 30) +
theme_minimal() +
labs(x = 'Child Poverty (%)',
y = 'Density', title = "Density plot of Michigan and Ohio") +
scale_fill_brewer(palette = 'Dark2') +
scale_color_discrete(name = 'State',
labels = c('Michigan','Ohio'))


```

